Curriculum and Imitation Learning for Biped Locomotion on Rough Terrain

### 2019-02-02 paper/rss/main.tex
Forgot to commit the figures earlier

For each approach (CIM and baseline) we run the experiment from scratch with four different starting random seeds.
Results on the 2D-Easy environment are shown in Fig. \ref{fig:ars baseline}.
The X axis shows the total number of simulated footsteps taken during training, and the Y axis shows total reward.
We plot the median and 5th/95th percentiles over 32 testing episodes (eight episodes for each of the four starting random seeds).

@@

Results on the 2D-Hard environment are shown in Fig. \ref{fig:nocur baseline}.
Like in Fig. \ref{fig:ars baseline},
we plot the median reward and 5th/95th percentiles over 32 testing episodes.

>>>>

For each approach (CIM and baseline) we run the experiment from scratch with four different starting random seeds.
Results on the 2D-Easy environment are shown in Fig. \ref{fig:ars baseline}.
The X axis shows the total number of simulated footsteps taken during training, and the Y axis shows total reward.
We plot the median and 10th/90th percentiles over 32 testing episodes (eight episodes for each of the four starting random seeds).

@@

Results on the 2D-Hard environment are shown in Fig. \ref{fig:nocur baseline}.
Like in Fig. \ref{fig:ars baseline},
we plot the median reward and 10th/90th percentiles over 32 testing episodes.
